Automatic Matching of Bullet Lands

### 2015-12-29 imaging-paper.Rnw
ROC and AUC

rocs$variable <- factor(rocs$variable, levels=features)
qplot(`FALSE`, `TRUE`, data=rocs,  geom="line", group=type) + theme_bw() + geom_abline(linetype=2) + xlab("False negative rate") + 
  ylab("False positive rate") + facet_wrap(facets=~variable, ncol=4)
@
\caption{\label{fig:rocs}ROC curves for all of the features described in section~\ref{sec:algorithm}. \hh{XXX compare ROC curve of CMS against the other individual features -- ccf should be a lot more predictive than CMS. XXX}
\hh{XXX next steps: get rid of lower curve. find area under the curve, put value on bottom right of the chart, sort by ROC.}}
\end{figure}

>>>>

aucs <- plyr::ldply(features, function(x) {
  subbstats <- subset(bstats, flagged == FALSE)
  pos.scores <- sample(subbstats[which(subbstats$match),x], 5000, replace=TRUE)
  neg.scores <- sample(subbstats[which(!subbstats$match),x], 5000, replace=TRUE)
  data.frame(x, upper=mean(pos.scores > neg.scores), 
             lower = mean(pos.scores < neg.scores))
})
aucs <- melt(aucs, measure.var=c("lower", "upper"))
names(aucs) <- c("variable", "type", "auc")
rocs <- merge(rocs, aucs, by=c("variable", "type"))
labels <- unique(subset(rocs, auc > 0.5)[,c("variable", "auc")])
labels$labels <- paste("AUC:", labels$auc)
labels$type <- NA

rocs$variable <- reorder(rocs$variable, -rocs$auc, min)
qplot(`FALSE`, `TRUE`, data=subset(rocs, auc > 0.5),  geom="line", group=type) + theme_bw() + geom_abline(linetype=2) + xlab("False negative rate") + 
  ylab("False positive rate") + facet_wrap(facets=~variable, ncol=4) + 
  geom_label(x=1, y=0, aes(label=labels), data=labels, hjust=1, vjust=0)
@
\caption{\label{fig:rocs}ROC curves for all of the features described in section~\ref{sec:algorithm}. Variables are sorted according to their area under the curve (AUC). Except for the distance $D$ between signatures, all features are more predictive than the maximal CMS. }
\end{figure}
